Hydra Battles and Cie

### 2021-08-21 doc/part-hydras.tex
conversion to Alectryon (chapter 5, half done)

\begin{Coqsrc}
Fixpoint iota (alpha : T1) : Hydra :=
  match alpha with
  | T1.zero => head
  | ocons gamma n beta => 
         node (hcons_mult (iota gamma) (S n) (iotas beta))
  end 
with iotas (alpha : T1) :  Hydrae :=
       match alpha with
       | T1.zero => hnil
       | ocons alpha0 n beta  => 
           hcons_mult (iota alpha0) (S n) (iotas beta)
       end.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma canonS_iota i alpha :
    nf alpha -> alpha <> 0 ->
    iota alpha -1-> iota (canon alpha (S i)).
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma path_to_battle alpha s beta :
  path_to  beta  s alpha -> nf alpha ->
  iota alpha -+-> iota beta.
\end{Coqsrc}

@@

\begin{Coqsrc}
Lemma LT_to_battle alpha beta :
    beta t1< alpha ->  iota alpha -+-> iota beta.
\end{Coqsrc}

@@

\begin{Coqsrc}
Class BoundedVariant {A:Type}{Lt:relation A}
      {Wf: well_founded Lt}{B : Battle}
      {m: Hydra -> A} (Var: Hvariant  Wf  B m)(mu:A):=
  {
  m_bounded: forall h, Lt (m h ) mu
  }.
\end{Coqsrc}

@@

\begin{Coqsrc}
Context (B: Battle)
          (mu: T1)
          (Hmu: nf mu)
          (m : Hydra -> T1)
          (Var : Hvariant  T1_wf B m)
          (Hy : BoundedVariant  Var mu).

  Hypothesis m_decrease : forall  i h h',
      round_n i h h'   -> m h' t1< m h.
\end{Coqsrc}

>>>>

\input{movies/snippets/O2H/iotaDef}

@@

\input{movies/snippets/O2H/canonSIota}

@@

\input{movies/snippets/O2H/pathToRoundPlus}

@@

\input{movies/snippets/O2H/LTToRoundPlus}

@@

\input{movies/snippets/Hydra_Definitions/BoundedVariant}

@@

\input{movies/snippets/Epsilon0_Needed_Generic/theContext}
